Dark matter halo concentrations with a bayesian approach

### 2014-05-25 paper/article.tex
new title

\title[Bayesian halo concentration]{Measurement of dark matter halo concentrations using a bayesian approach}
\author[Poveda \& Forero-Romero]{
\parbox[t]{\textwidth}{\raggedright
  Christian Poveda$^{1}$ \&
  Jaime E. Forero-Romero$^{1}$
}
\vspace*{6pt}\\
$^{1}$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
}
\maketitle

@@

\begin{equation}
\chi^2(c) = \sum_{i}[m_i - m(< x_i;c)]^2, 
\end{equation}
%
where $m(<x_i;c)$ corresponds to the values in Eq.(\ref{eq:profile}) at
$x=x_i$ and a given value of the concentration parameter $c$.

@@

\section{Numerical Experiments}
Finally we compare this results with the values obtaned by BDM, since
the number of halos obtained by FOF and BDM is different, each BDM
halo gets related with the nearest halo in FOF. We compute two
concentrations, one where the overdensity limit is $360\rho_{back}$
(like in BDMV) an other where the overdensity limit is
$740\rho_{back}$ (like in BDMW).

\subsection{Mock Data and Simulations}
\label{sec:data}
\section{Results}
\label{sec:results}

\subsection{Trial Problem with several Generated Halos}

Several halos with known values of $c$ were generated. These halos
were then processed to determine the acurracy of this method. The
number of particles and value of $c$ for each halo were generated
randomly.  
\begin{figure}[H]
\caption{FIXME: Test results}
\end{figure}

\subsection{Results from the simulations}

\subsection{What kind of implications (Low resolution simulations, other fitting algorithms)}

@@

>>>>

\title[Bayesian halo concentrations]{Dark matter halo
  concentrations with a bayesian approach}
\author[Poveda \& Forero-Romero]{
\parbox[t]{\textwidth}{\raggedright
  Christian Poveda$^{1}$ \&
  Jaime E. Forero-Romero$^{1}$
}
\vspace*{6pt}\\
$^{1}$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
}
\maketitle

@@

\begin{equation}
\chi^2(c) = \sum_{i}[\log m_i - \log m(< x_i;c)]^2, 
\end{equation}
%
where $m(<x_i;c)$ corresponds to the values in Eq.(\ref{eq:profile}) at
$x=x_i$ and a given value of the concentration parameter $c$.

@@

\section{Numerical Experiments}

\subsection{Mock Halos}
Several halos with known values of $c$ were generated. These halos
were then processed to determine the acurracy of this method. The
number of particles and value of $c$ for each halo were generated
randomly.

\subsection{Simulation Data}
\label{sec:data}

\section{Results}
\label{sec:results}

Finally we compare this results with the values obtaned by BDM, since
the number of halos obtained by FOF and BDM is different, each BDM
halo gets related with the nearest halo in FOF. We compute two
concentrations, one where the overdensity limit is $360\rho_{back}$
(like in BDMV) an other where the overdensity limit is
$740\rho_{back}$ (like in BDMW).

\subsection{Mock Halos}
\begin{figure}[H]
\caption{FIXME: Test results}
\end{figure}

\subsection{Simulation Dat}

@@

\subsection{Comparison against other methods}

\subsection{Concentration as a function of halo mass}

\subsection{Implication for comparison against observations}
